\documentclass[11pt,a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[margin=1.8cm]{geometry}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1.5pt}
\setlength{\emergencystretch}{2em}
\linespread{0.94}
\definecolor{sectionblue}{RGB}{47,126,181}
\newcommand{\letterheading}[1]{\textbf{\textcolor{sectionblue}{#1}}}
\setlist[itemize]{
  leftmargin=5.5mm,
  itemsep=0pt,
  topsep=0.5pt,
  parsep=0pt,
  partopsep=0pt
}

\begin{document}

\begin{flushright}
\textbf{St\'ephane Ga\"el R. Ekodeck}\\
Department of Computer Science, University of Yaound\'e I, Cameroon\\
\href{mailto:stephane-gael.ekodeck@facsciences-uy1.cm}
{stephane-gael.ekodeck@facsciences-uy1.cm}\\
June 8, 2026
\end{flushright}

\vspace{-4mm}
The Editor-in-Chief\\
\emph{Journal of Visual Communication and Image Representation}\\
Elsevier

\textbf{Dear Editor-in-Chief,}

We respectfully submit our manuscript, \textbf{``Net-Aware Learned Block
Mapping for Reversible Data Hiding in Binary Images,''} for consideration as
a \textbf{Research Article} in the \emph{Journal of Visual Communication and
Image Representation}.

\letterheading{Scope Fitness Assessment.}
The manuscript addresses reversible visual-data representation in binary
images through perceptual distortion control, exact restoration, learned
content analysis, and auditable payload measurement:
\begin{itemize}
  \item \textbf{Image representation problem:} application data are embedded
  in binary images with bitwise recovery of the message and original cover.
  \item \textbf{Technical contribution:} globally injective distance-one
  substitutions, CNN perceptual ranking, and enumerative coding measure useful
  capacity after serialized metadata.
  \item \textbf{Common protocol:} ABM, PPOCP, Huynh--Nguyen, and Dong use
  identical covers, messages, payloads, distortion, accounting, and
  round-trip checks.
\end{itemize}

\letterheading{Scientific Novelty and Evidence.}
The central contribution is the systematic criterion
$C_{\mathrm{net}}=C_{\mathrm{gross}}-|A_{\mathrm{wire}}|$, which prevents
side information from being excluded from capacity claims. Eight-fold
leave-one-image-out validation covers 13,808 candidates ($r=0.989$); held-out
placement reduces mean DRD from 0.8054 to 0.7663 (4.85\%) and improves every
document image. The mapping layer carries 2245 net bits on average on eight
document benchmarks and reaches the highest observed net-payload operating
point on matched BOSSbase images. Availability, Holm-corrected inference,
runtime, memory, and grouped steganalysis are also reported.

\letterheading{Practical and Reproducibility Value.}
The work provides reversibility proofs, deterministic algorithms, an exact
wire format, model weights, tests, per-image results, plotting scripts, and
fixed seeds. The reproducibility package is available at
\href{https://github.com/EkodeckStephane/net-aware-block-mapping-rdh}
{github.com/EkodeckStephane/net-aware-block-mapping-rdh}.

\letterheading{Mandatory Author Declarations.}
\begin{itemize}
  \item \textbf{Originality and exclusivity:} the manuscript is original,
  unpublished, and not under consideration elsewhere.
  \item \textbf{Author approval:} all authors approved the manuscript,
  authorship order, contributions, and submission.
  \item \textbf{Interests and funding:} there are no competing interests or
  external funding.
  \item \textbf{Ethics:} no humans, animals, clinical interventions, or
  sensitive personal data are involved.
\end{itemize}

The manuscript will interest JVCIR readers working on image representation,
reversible data hiding, perceptual quality, and learned image analysis. Thank
you for considering our submission.

\begin{center}
Yours sincerely,
\end{center}

\vspace{1mm}
\textbf{St\'ephane Ga\"el R. Ekodeck} (First and Corresponding Author)\\
ORCID: 0000-0002-8094-8832\\
Department of Computer Science, University of Yaound\'e I, Cameroon\\
\href{mailto:stephane-gael.ekodeck@facsciences-uy1.cm}
{stephane-gael.ekodeck@facsciences-uy1.cm}\\
\textbf{Co-authors:} Vivien Beyala Kamgang, Serge Alain Eb\'el\'e,
and Julius Marcellin Nkenlifack.

\end{document}
